An Evolutionary Algorithm for the Multiobjective Risk-Equity Constrained Routing Problem

### 2011-11-30 DAW_hazmatHypE/trunk/paper/hazmatRouting_EvolOptim.tex
wrote HypE part

\subsection{The HypE and NSGA-II Selectors of PISA}
\TODO{write}

>>>>

\subsection{Hypervolume Estimation Algorithm for Multiobjective Optimization: The HypE Selector of PISA}
In order to fully describe the proposed EMO algorithm for the multiobjective risk-equity constrained routing problem, we briefly mention the working principles of the HypE selection. The main purpose of an EMO algorithm's environmental selection is to ensure convergence of the population towards the Pareto front as well as a good spread of it along the front \citep{deb2001a}. HypE persues these two goals by a two-step approach based on the hypervolume indicator \citep[see][]{ztlf2003a}.

Given the $\mu$ solutions of the old population and the $\lambda$ new ones, the best $\mu$ of them are chosen in the following way. First, a non-dominated sorting \citep{gold1989a} is performed---identifying sets of non-dominated fronts with different ranks. The solutions that are not dominated in the entire set get a rank of 1, the solutions of rank 2 are those which are non-dominated among the remaining solutions, and so forth. As long as the number of solutions is not exceeding $\mu$, entire fronts are chosen for the next iteration starting from the front with rank 1. For the first front for which the overall number of solutions exceeds $\mu$, a second criterion is used to determine the solutions to be kept for the next iteration. This decision is made according to the (expected) loss in hypervolume, which is a criterion that is refining the underlying Pareto dominance relation \citep{ztb2010a}---the main reason why many recent EMO algorithms employ the hypervolume indicator.
